---
title: "Descriptive Statistics: Replication Paper"
subtitle: "ESS 2002 - 2010 (Five Waves)"
author: "IICP Research Team"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plm) # fixed effect
library(ggplot2)
library(interplot)
```

```{r ess, echo=FALSE, message=FALSE, warning=FALSE}
ess_2002 = haven::read_stata("ESS1e06_6.dta")
ess_2004 = haven::read_stata("ESS2e03_6.dta")
ess_2006 = haven::read_stata("ESS3e03_7.dta")
ess_2008 = haven::read_stata("ESS4e04_5.dta")
ess_2010 = haven::read_stata("ESS5e03_4.dta")
```

```{r ess_yr, echo=FALSE, message=FALSE, warning=FALSE}
ess_2002 = ess_2002 %>% 
  dplyr::select(essround, cntry, agea, blgetmg, brncntr, ctzcntr, livecntr, cntbrth, gndr, edulvla, facntr, mocntr, polintr, polcmpl, poldcs, hincfel, uempla, ppltrst, pplfair, imsmetn, imdfetn, impcntr, imbgeco, imueclt, imwbcnt, hinctnt) %>%
  plyr::rename(c("cntbrth"="birthplace","blgetmg"="ethnic", "edulvla"="edu", "brncntr"="fborn","imsmetn"="sameim", "imdfetn"="diffim", "impcntr"="poorim", "imbgeco"="ecoim", "imueclt"="cultim", "imwbcnt"="liveim"))
  ess_2002 = ess_2002 %>% mutate(hinctnt = hinctnt/12*10) # rescale to fit data from 2008 and 2010
ess_2004 = ess_2004 %>% 
  dplyr::select(essround, cntry, agea, blgetmg, brncntr, ctzcntr, livecntr, cntbrtha, gndr, edulvla, facntr, mocntr, polintr, polcmpl, poldcs, hincfel, uempla, ppltrst, pplfair,imsmetn, imdfetn, impcntr, imbgeco, imueclt, imwbcnt, hinctnt) %>%
  plyr::rename(c("cntbrtha"="birthplace","blgetmg"="ethnic", "edulvla"="edu", "brncntr"="fborn","imsmetn"="sameim", "imdfetn"="diffim", "impcntr"="poorim", "imbgeco"="ecoim", "imueclt"="cultim", "imwbcnt"="liveim"))
  ess_2004 = ess_2004 %>% mutate(hinctnt = hinctnt/12*10)
ess_2006 = ess_2006 %>% 
  dplyr::select(essround, cntry, agea, blgetmg, brncntr, ctzcntr, livecntr, cntbrtha, gndr, edulvla, facntr, mocntr, polintr, polcmpl, poldcs, hincfel, uempla, ppltrst, pplfair, imsmetn, imdfetn, impcntr, imbgeco, imueclt, imwbcnt, hinctnt) %>%
  plyr::rename(c("cntbrtha"="birthplace","blgetmg"="ethnic", "edulvla"="edu", "brncntr"="fborn","imsmetn"="sameim", "imdfetn"="diffim", "impcntr"="poorim", "imbgeco"="ecoim", "imueclt"="cultim", "imwbcnt"="liveim"))
  ess_2006 = ess_2006 %>% mutate(hinctnt = hinctnt/12*10)
ess_2008 = ess_2008 %>% 
  dplyr::select(essround, cntry, agea, blgetmg, brncntr, ctzcntr, livecntr, cntbrthb, gndr, edulvla, facntr, mocntr, polintr, polcmpl, poldcs, hincfel, uempla, ppltrst, pplfair, imsmetn, imdfetn, impcntr, imbgeco, imueclt, imwbcnt, hinctnta) %>%
  plyr::rename(c("cntbrthb"="birthplace","blgetmg"="ethnic", "edulvla"="edu", "brncntr"="fborn","imsmetn"="sameim", "imdfetn"="diffim", "impcntr"="poorim", "imbgeco"="ecoim", "imueclt"="cultim", "imwbcnt"="liveim", "hinctnta" = "hinctnt"))
ess_2010 = ess_2010 %>% 
  dplyr::select(essround, cntry, agea, blgetmg, brncntr, ctzcntr, livecnta, cntbrthb, gndr, edulvlb, facntr, mocntr, polintr, hincfel, uempla, ppltrst, pplfair, imsmetn, imdfetn, impcntr, imbgeco, imueclt, imwbcnt, hinctnta) %>%
  plyr::rename(c("cntbrthb"="birthplace","blgetmg"="ethnic", "livecnta" = "livecntr","edulvlb"="edu", "brncntr"="fborn","imsmetn"="sameim", "imdfetn"="diffim", "impcntr"="poorim", "imbgeco"="ecoim", "imueclt"="cultim", "imwbcnt"="liveim", "hinctnta" = "hinctnt"))
  ess_2010$livecntr = ess_2010$livecntr - 2010
  ess_2010$livecntr = ifelse(ess_2010$livecntr >= 1, 1,
                           ifelse(ess_2010$livecntr %in% c(-1:-5), 2,
                                  ifelse(ess_2010$livecntr %in% c(-6:-10), 3,
                                         ifelse(ess_2010$livecntr %in% c(-11:-20), 4,
                                                ifelse(ess_2010$livecntr < -20, 5, NA)))))
  ess_2010$polcmpl = NA
  ess_2010$poldcs = NA

ess_2002 = haven::zap_labels(ess_2002)
ess_2010 = haven::zap_labels(ess_2010)
```

```{r ess_civix, echo=FALSE, message=FALSE, warning=FALSE}
ess_raw = rbind(ess_2002, ess_2004, ess_2006, ess_2008, ess_2010)
ess_raw$sec.immi = ifelse(ess_raw$facntr == 2 | ess_raw$mocntr == 2, 1, 0)
ess_raw$ethnic = ifelse(ess_raw$ethnic == 1, 1,
                        ifelse(ess_raw$ethnic == 2, 0, NA))
ess_raw$citizen = ifelse(ess_raw$ctzcntr == 1, 1,
                         ifelse(ess_raw$ctzcntr == 2, 0, NA))
ess_raw$residence = ifelse(ess_raw$livecntr <= 3, 1, 0) # 1 = lived less than 10 yrs, 0 = lived more than 10 yrs
ess_raw$fborn = ifelse(ess_raw$fborn == 1, 0, 1) # now 1 as foreign born, 0 as native born
ess_raw$birthplace = ifelse(ess_raw$birthplace %in% c(66,77,88,99,"02","03","04","06"), NA, ess_raw$birthplace)
  ess_raw = ess_raw[complete.cases(ess_raw$birthplace),]
  eu_member = c("BE", "FR", "DE", "IT", "LU", "NL", "DK", "IE", "GB", "GR", "PT", "ES","AT","SE")
ess_raw$eubirth = ifelse(ess_raw$birthplace %in% eu_member, 1, 0)
ess_raw$female = ifelse(ess_raw$gndr == 2, 1, 
                        ifelse(ess_raw$gndr == 1, 0, NA))
ess_raw$edu = ifelse(ess_raw$edu > 5, NA, ess_raw$edu)

ess_raw$polintr = ifelse(ess_raw$polintr > 4, NA, ess_raw$polintr)
# table(ess_raw$polcmpl) whether politics are too complicated to understand, 5 as always, 1 as never
# table(ess_raw$poldcs) how difficult it is to make mind up about political issues, 5 as very easy, 1 as very difficult
ess_raw$poldcs = ifelse(ess_raw$poldcs == 5, 1, # now 1 as easy
                        ifelse(ess_raw$poldcs == 4, 2, 
                               ifelse(ess_raw$poldcs == 3, 3, 
                                      ifelse(ess_raw$poldcs == 2, 4, 
                                             ifelse(ess_raw$poldcs == 1, 5, ess_raw$poldcs))))) # 5 as difficult
ess_raw$hincfel = ifelse(ess_raw$hincfel > 4, NA, ess_raw$hincfel)
ess_raw$ppltrst = ifelse(ess_raw$ppltrst > 10, NA, ess_raw$ppltrst) # 0 as can't be too careful, 10 as most people can be trusted
ess_raw$pplfair = ifelse(ess_raw$pplfair > 10, NA, ess_raw$pplfair) # 0 as most people take advantage, 10 as most people are fair
ess_raw$employ = ifelse(ess_raw$uempla == 0, 1, 0) # 1 = employed, 0 = unemployed
```

```{r anti-immigrant, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
ess_raw <- ess_raw %>%
  group_by(cntry) %>%
  mutate(sameimavg = mean(sameim, na.rm = T))
ess_raw <- ess_raw %>%
  group_by(cntry) %>%
  mutate(diffimavg = mean(diffim, na.rm = T))
ess_raw <- ess_raw %>%
  group_by(cntry) %>%
  mutate(poorimavg = mean(poorim, na.rm = T))
ess_raw$anti1 = (ess_raw$sameimavg + ess_raw$diffimavg + ess_raw$poorimavg)/3 
ess_raw$anti3 = (ess_raw$sameimavg + ess_raw$diffimavg + ess_raw$poorimavg)/3 / 4 * 10 # rescale

ess_raw = ess_raw %>% mutate(
  anti.b = ifelse(anti1 > 2.230, 1, 0)
)

ess_raw$ecoim <- as.numeric(ess_raw$ecoim)
library(car)
# ess_raw$ecoim = recode(ess_raw$ecoim,'0=10; 1=9; 2=8; 3=7; 4=6; 5=5; 6=4; 7=3; 8=2; 9=1; 10=0')
ess_raw <- ess_raw %>%
  group_by(cntry) %>%
  mutate(ecoimavg = mean(ecoim, na.rm = T))

ess_raw$cultim <- as.numeric(ess_raw$cultim)
# library(car)
# ess_raw$cultim = recode(ess_raw$cultim,'0=10; 1=9; 2=8; 3=7; 4=6; 5=5; 6=4; 7=3; 8=2; 9=1; 10=0')
ess_raw <- ess_raw %>%
  group_by(cntry) %>%
  mutate(cultimavg = mean(cultim, na.rm = T))

ess_raw$liveim <- as.numeric(ess_raw$liveim)
# library(car)
# ess_raw$liveim = recode(ess_raw$liveim,'0=10; 1=9; 2=8; 3=7; 4=6; 5=5; 6=4; 7=3; 8=2; 9=1; 10=0')
ess_raw <- ess_raw %>%
  group_by(cntry) %>%
  mutate(liveimavg = mean(liveim, na.rm = T))
ess_raw$anti2 = (ess_raw$ecoimavg + ess_raw$cultimavg + ess_raw$liveimavg)/3
```

```{r civix, message=FALSE, warning=FALSE, echo=FALSE}
# civix.cntry = c("AT", "BE", "DK", "FI", "FR", "DE", "GR", "IE", "NL", "PT", "ES", "SE", "GB")
#   civix.sc =   as.numeric( c(5.5, 1.25, 8.25,  2.5,    5,     7, 5.25,    1, 6.25, 1.25, 2.5, 0, 5.5))
#   civix.1 = as.data.frame(t(rbind(civix.cntry, civix.sc)))
#   colnames(civix.1) = c("cntry", "civix")
#   civix.1$civix = as.numeric(civix.1$civix)
library(readxl)
civix.1 = read_xlsx("CIVIXscores.xlsx")
# table(civix.1$cntry)

ess_raw = ess_raw %>% left_join(civix.1, by = 'cntry') 
ess_raw = ess_raw %>% mutate(civix.d = ifelse(civix > 2.5, 1, 0))
```

```{r mean, message=FALSE, warning=FALSE, echo=FALSE}
ess_mean = ess_raw %>% filter(citizen == 1) %>% group_by(cntry) %>% 
  dplyr::select(cntry,polintr, hincfel, employ, ppltrst, pplfair, polcmpl, poldcs, hinctnt) %>%
  summarise(mean.poli = mean(polintr, na.rm = TRUE),
            mean.employ = mean(employ, na.rm = TRUE),
            mean.hincfel = mean(hincfel, na.rm = TRUE),
            mean.ppltrst = mean(ppltrst, na.rm = TRUE),
            mean.pplfair = mean(pplfair, na.rm = TRUE),
            mean.polcmpl = mean(polcmpl, na.rm = TRUE),
            mean.poldcs = mean(poldcs, na.rm = TRUE),
            mean.hinctnt = mean(hinctnt, na.rm = TRUE))

ess_tenyr = ess_raw %>% filter(residence == 1)

ess_tenyr = ess_tenyr %>% left_join(ess_mean, by='cntry')
ess_raw = ess_raw %>% left_join(ess_mean, by='cntry')

ess_tenyr = ess_tenyr %>% mutate(
  poli.gap = polintr - mean.poli, 
  employ.gap = employ - mean.employ,
  hincfel.gap = hincfel - mean.hincfel, 
  ppltrst.gap = ppltrst - mean.ppltrst,
  pplfair.gap = pplfair - mean.pplfair, 
  polcmpl.gap = polcmpl - mean.polcmpl,
  poldcs.gap = poldcs - mean.poldcs,
  hinctnt.gap = hinctnt - mean.hinctnt
  )

ess_h.tenyr = ess_tenyr %>% filter(civix.d == 1)
ess_l.tenyr = ess_tenyr %>% filter(civix.d == 0)

ess_anti.h = ess_tenyr %>% filter(anti1 > 2.230)
ess_anti.l = ess_tenyr %>% filter(anti1 <= 2.230)

ess_hh = ess_tenyr %>% filter(civix.d == 1 & anti1 > 2.230)
ess_hl = ess_tenyr %>% filter(civix.d == 1 & anti1 <= 2.230)
ess_lh = ess_tenyr %>% filter(civix.d == 0 & anti1 > 2.230)
ess_ll = ess_tenyr %>% filter(civix.d == 0 & anti1 <= 2.230)
```

# Notes

* There is a variation in sample sizes across countries. It's likely that a lot of the results are driven by a few countries 
  + Very large sample size in Spain (ES) and Ireland (IE), both countries have lower CIVIX scores
  + Very small sample size in Italy (IT) and Finland (FI); Italy with a high CIVIX score and Finland with a low one
  + Question about residency and citizenship was not widely asked in Italy from 2006 to 2010 (latest three waves)
* All the distributions of the outcome variables are for immigrants (those who have lived in the countrt for less than 10 years)
* We also included all the regression models FYI

# Descriptive Statistics

## Sample Size 

### 10 years of residence

```{r sample size, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
ess_raw %>% filter(civix.d == 1) %>% # mutate(residence = as.factor(residence)) %>% na.omit(residence) %>%
ggplot(aes(x = residence)) +
 geom_histogram(binwidth = 0.5, stat = "count") + 
  stat_bin(binwidth = 0.5, stat = "count", geom = "text", colour = "white", size = 3.5,
            aes(label = ..count..),position=position_stack(vjust=0.5)) +
  # scale_x_continuous("Immigrants by residence (less than 10 years)", labels = c("0" = "Natives", "1" = "Immigrants")) +
  facet_wrap(~cntry, nrow = 2) +
  xlab("Immigrants by residence (less than 10 years); 0 = Natives, 1 = Immigrants") +
  ggtitle("Sample Size in Countries with High CIVIX Scores, ESS 2002 - 2010")

# ggsave("high.civix.sample.jpeg")

ess_raw %>% filter(civix.d == 0) %>% # mutate(residence = as.factor(residence)) %>% na.omit(residence) %>%
ggplot(aes(x = residence)) +
 geom_histogram(binwidth = 0.5, stat = "count") + 
  stat_bin(binwidth = 0.5, stat = "count", geom = "text", colour = "white", size = 3.5,
            aes(label = ..count..),position=position_stack(vjust=0.5)) +
  # scale_x_continuous("Immigrants by residence (less than 10 years)", labels = c("0" = "Natives", "1" = "Immigrants")) +
  facet_wrap(~cntry, nrow = 2) +
  xlab("Immigrants by residence (less than 10 years); 0 = Natives, 1 = Immigrants") +
  ggtitle("Sample Size in Countries with Low CIVIX Scores, ESS 2002 - 2010")

# ggsave("low.civix.sample.jpeg")
```

<a href="#top">Back to top</a>

### Sample Size: citizenship

```{r sample size citizenship, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
ess_raw %>% filter(civix.d == 1) %>% # mutate(residence = as.factor(residence)) %>% na.omit(residence) %>%
ggplot(aes(x = citizen)) +
 geom_histogram(binwidth = 0.5, stat = "count") + 
  stat_bin(binwidth = 0.5, stat = "count", geom = "text", colour = "white", size = 3.5,
            aes(label = ..count..),position=position_stack(vjust=0.5)) +
  # scale_x_continuous("Immigrants by residence (less than 10 years)", labels = c("0" = "Natives", "1" = "Immigrants")) +
  facet_wrap(~cntry, nrow = 2) +
  xlab("Immigrants by citizenship; 0 = Non-citizens, 1 = Citizens") +
  ggtitle("Sample Size in Countries with High CIVIX Scores, ESS 2002 - 2010")

# ggsave("high.civix.sample.jpeg")

ess_raw %>% filter(civix.d == 0) %>% # mutate(residence = as.factor(residence)) %>% na.omit(residence) %>%
ggplot(aes(x = citizen)) +
 geom_histogram(binwidth = 0.5, stat = "count") + 
  stat_bin(binwidth = 0.5, stat = "count", geom = "text", colour = "white", size = 3.5,
            aes(label = ..count..),position=position_stack(vjust=0.5)) +
  # scale_x_continuous("Immigrants by residence (less than 10 years)", labels = c("0" = "Natives", "1" = "Immigrants")) +
  facet_wrap(~cntry, nrow = 2) +
  xlab("Immigrants by citizenship; 0 = Non-citizens, 1 = Citizens") +
  ggtitle("Sample Size in Countries with Low CIVIX Scores, ESS 2002 - 2010")

# ggsave("low.civix.sample.jpeg")
```

<a href="#top">Back to top</a>

## Outcome Variable: Political Interest

* 1 as very interested, 4 as not at all

### Absolute Value (Political Interest)

```{r polintr des, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
  ggplot(data = ess_h.tenyr, aes(x = polintr)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Political Interest") +
  ggtitle("Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = polintr)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Political Interest") +
  ggtitle("Countries with Low CIVIX Scores")
 
# ggsave("low.civix.polintr.jpeg")
```

### Gap with Native Citizens (Political Interest)

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
 ggplot(data = ess_h.tenyr, aes(x = poli.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Political Interest (Gap)") +
  ggtitle("Distribution across Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = poli.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Political Interest (gap)") +
  ggtitle("Distribution across Countries with Low CIVIX Scores")
```

<a href="#top">Back to top</a>

```{r polintr mean, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8, include=FALSE}
# ess_tenyr = ess_tenyr[order(ess_tenyr$mean.poli)]
# ess_raw$mean.poli = with(ess_raw, reorder(mean.poli, cntry))



# ess_tenyr %>% dplyr::select(mean.poli, polintr, civix.d, cntry, poli.gap) %>% 
#   group_by(cntry) %>% # order_by(.,mean.poli, call = ) %>%
#   na.omit(civix.d) %>%  # arrange(polintr) %>% nest(cntry) 
#   # mutate(mean.poli = factor(round(mean.poli, digits = 2), levels = mean.poli)) %>%
#   ggplot(aes(x = reorder(cntry, -poli.gap), y = poli.gap,  color = as.factor(civix.d))) + 
#   # geom_point() + 
#   geom_pointrange()
```

## Outcome Variable: Politics are complicated

* 1 as never, 5 as frequently

### Absolute Value (Political Sophistication)

```{r polcmpl des, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
  ggplot(data = ess_h.tenyr, aes(x = polcmpl)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Political Sophistication") +
  ggtitle("Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = polcmpl)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Political Sophistication") +
  ggtitle("Countries with Low CIVIX Scores")
 
# ggsave("low.civix.polintr.jpeg")
```

### Gap with Native Citizens (Political Sophistication)

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
 ggplot(data = ess_h.tenyr, aes(x = polcmpl.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Political Sophistication (Gap)") +
  ggtitle("Distribution across Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = polcmpl.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Political Sophistication (gap)") +
  ggtitle("Distribution across Countries with Low CIVIX Scores")
```

<a href="#top">Back to top</a>

## Outcome Variable: Difficult to make political decisions

* 1 as very difficult, 5 as very easy

### Absolute Value (Political decisions)

```{r poldcs des, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
  ggplot(data = ess_h.tenyr, aes(x = poldcs)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Political decisions") +
  ggtitle("Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = poldcs)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Political decisions") +
  ggtitle("Countries with Low CIVIX Scores")
 
# ggsave("low.civix.polintr.jpeg")
```

### Gap with Native Citizens (Political decisions)

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
 ggplot(data = ess_h.tenyr, aes(x = poldcs.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Political decisions (Gap)") +
  ggtitle("Distribution across Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = poldcs.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Political decisions (gap)") +
  ggtitle("Distribution across Countries with Low CIVIX Scores")
```

<a href="#top">Back to top</a>

## Outcome Variable: Subjective Financial Situations

### Absolute Value 

```{r hincfel des, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
  ggplot(data = ess_h.tenyr, aes(x = hincfel)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Subjective Financial Situations") +
  ggtitle("Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = hincfel)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Subjective Financial Situations") +
  ggtitle("Countries with Low CIVIX Scores")
 
# ggsave("low.civix.polintr.jpeg")
```

### Gap with Native Citizens (Subjective Financial Situations)

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
 ggplot(data = ess_h.tenyr, aes(x = hincfel.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Subjective Financial Situations (Gap)") +
  ggtitle("Distribution across Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = hincfel.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Subjective Financial Situations (gap)") +
  ggtitle("Distribution across Countries with Low CIVIX Scores")
```

<a href="#top">Back to top</a>

## Outcome Variable: Employment

* 1 as employed, 0 as unemployed 

### Absolute Value (employment)

```{r employ des, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
  ggplot(data = ess_h.tenyr, aes(x = employ)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Employment") +
  ggtitle("Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = employ)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Employment") +
  ggtitle("Countries with Low CIVIX Scores")
 
# ggsave("low.civix.polintr.jpeg")
```

### Gap with Native Citizens (employment)

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
 ggplot(data = ess_h.tenyr, aes(x = employ.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("Employment (Gap)") +
  ggtitle("Distribution across Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = employ.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 3.5,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("Employment (gap)") +
  ggtitle("Distribution across Countries with Low CIVIX Scores")
```

<a href="#top">Back to top</a>

## Outcome Variable: General Trust

* "Most people can be trusted or you can't be too careful"
  + 0 as can't be too careful, 10 as most people can be trusted

### Absolute Value (Trust)

```{r trust des, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
  ggplot(data = ess_h.tenyr, aes(x = ppltrst)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white",  size = 2,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("General Trust") +
  ggtitle("Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = ppltrst)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white",  size = 2,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("General Trust") +
  ggtitle("Countries with Low CIVIX Scores")
 
# ggsave("low.civix.polintr.jpeg")
```

### Gap with Native Citizens (General Trust)

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
 ggplot(data = ess_h.tenyr, aes(x = ppltrst.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white",  size = 2,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("General Trust (Gap)") +
  ggtitle("Distribution across Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = ppltrst.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white",  size = 2,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("General Trust (gap)") +
  ggtitle("Distribution across Countries with Low CIVIX Scores")
```

<a href="#top">Back to top</a>

## Outcome Variable: People being fair

* "Most people try to take advantage of you, or try to be fair"
  + 0 as most people take advantage, 10 as most people are fair

### Absolute Value (People being fair)

```{r pplfair des, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
  ggplot(data = ess_h.tenyr, aes(x = pplfair)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 2,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("People being fair") +
  ggtitle("Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = pplfair)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white", size = 2,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("People being fair") +
  ggtitle("Countries with Low CIVIX Scores")
 
# ggsave("low.civix.polintr.jpeg")
```

### Gap with Native Citizens (People being fair)

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8}
 ggplot(data = ess_h.tenyr, aes(x = pplfair.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white",  size = 2,
           aes(label = ..count..),position=position_stack(vjust=0.5)) +
  facet_wrap(~cntry, nrow = 2) + 
  xlab("People being fair (Gap)") +
  ggtitle("Distribution across Countries with High CIVIX Scores")

# ggsave("high.civix.polintr.jpeg")

 ggplot(data = ess_l.tenyr, aes(x = pplfair.gap)) + 
  geom_histogram(binwidth = 1)  + 
  stat_bin(binwidth = 1, geom = "text", colour = "white",  size = 2,
           aes(label = ..count..),position=position_stack(vjust=0.5)) + 
  facet_wrap(~cntry, nrow = 2)+ 
  xlab("People being fair (gap)") +
  ggtitle("Distribution across Countries with Low CIVIX Scores")
```

<a href="#top">Back to top</a>

# Regression Models for Different Outcomes

## Political Interest

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8, results='asis'}
polintr.1 = lm(polintr ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polintr.1)
polintr.2 = lm(poli.gap ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polintr.2)

stargazer::stargazer(header = FALSE, polintr.1, polintr.2,
                     type = "html", 
                     covariate.labels = c("CIVIX", "Age", "Ethnic Minority",
                               "Female", "Born in EU", "Citizen"),
                     column.labels   = c("Abs", "Gap"))
```

<a href="#top">Back to top</a>

## Politics are Complicated

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8, results='asis'}
polcmpl.1 = lm(polcmpl ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polcmpl.1)
polcmpl.2 = lm(polcmpl.gap ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polintr.2)

stargazer::stargazer(header = FALSE, polcmpl.1, polcmpl.2,
                     type = "html", 
                     covariate.labels = c("CIVIX", "Age", "Ethnic Minority",
                               "Female", "Born in EU", "Citizen"),
                     column.labels   = c("Abs", "Gap"))
```

<a href="#top">Back to top</a>

## Difficult to make decisions abotu politics

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8, results='asis'}
poldcs.1 = lm(poldcs ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polcmpl.1)
poldcs.2 = lm(poldcs.gap ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polintr.2)

stargazer::stargazer(header = FALSE, poldcs.1, poldcs.2,
                     type = "html", 
                     covariate.labels = c("CIVIX", "Age", "Ethnic Minority",
                               "Female", "Born in EU", "Citizen"),
                     column.labels   = c("Abs", "Gap"))
```

<a href="#top">Back to top</a>

## Subjective Financial Situations

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8, results='asis'}
hincfel.1 = lm(hincfel ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polcmpl.1)
hincfel.2 = lm(hincfel.gap ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polintr.2)

stargazer::stargazer(header = FALSE, hincfel.1, hincfel.2,
                     type = "html", 
                     covariate.labels = c("CIVIX", "Age", "Ethnic Minority",
                               "Female", "Born in EU", "Citizen"),
                     column.labels   = c("Abs", "Gap"))
```

<a href="#top">Back to top</a>

## Employment

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8, results='asis'}
employ.1 = glm(employ ~ civix.d + agea + ethnic + female + edu + eubirth + citizen, family = "binomial" , data = ess_tenyr)
# summary(polcmpl.1)
employ.2 = lm(employ.gap ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polintr.2)

stargazer::stargazer(header = FALSE, employ.1, employ.2,
                     type = "html", 
                     covariate.labels = c("CIVIX", "Age", "Ethnic Minority",
                               "Female", "Born in EU", "Citizen"),
                     column.labels   = c("Abs (Logit)", "Gap"))
```

<a href="#top">Back to top</a>

## General Trust

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8, results='asis'}
ppltrst.1 = lm(ppltrst ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polcmpl.1)
ppltrst.2 = lm(ppltrst.gap ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polintr.2)

stargazer::stargazer(header = FALSE, ppltrst.1, ppltrst.2,
                     type = "html", 
                     covariate.labels = c("CIVIX", "Age", "Ethnic Minority",
                               "Female", "Born in EU", "Citizen"),
                     column.labels   = c("Abs", "Gap"))
```

<a href="#top">Back to top</a>

## People being fair

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.height=4, fig.width=8, results='asis'}
pplfair.1 = lm(pplfair ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polcmpl.1)
pplfair.2 = lm(pplfair.gap ~ civix.d + agea + ethnic + female + edu + eubirth + citizen , data = ess_tenyr)
# summary(polintr.2)

stargazer::stargazer(header = FALSE, pplfair.1, pplfair.2,
                     type = "html", 
                     covariate.labels = c("CIVIX", "Age", "Ethnic Minority",
                               "Female", "Born in EU", "Citizen"),
                     column.labels   = c("Abs", "Gap"))
```

<a href="#top">Back to top</a>
